Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)

### 2018-10-31 GSV-comment-brief.Rmd
update Rmd

---
title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
output:
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  bookdown::tufte_book2:
    citation_package: natbib
    latex_engine: xelatex
    md_extensions: +raw_attribute
bibliography: bibliography.bib
link-citations: yes
abstract: |
  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution   of the number of liars in "coin flip" style experiments. However, their method gives 
  erroneous confidence intervals. I explain why and describe two better
  ways to calculate probability distributions.
---

@@

1. Do not use the GSV confidence intervals.
2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
  confidence intervals and tests.
3. If your N is too small for point 2 to apply, it may be too small, since results will 
  depend on methods used and on one's priors.
4. If increasing your N is not possible for whatever reason, consider using Bayesian methods to find
  confidence intervals and point estimates. To estimate differences between subgroups, consider
  empirical Bayes with a prior derived from the pooled sample.

>>>>

---
title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
output:
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  bookdown::tufte_book2:
    citation_package: natbib
    latex_engine: xelatex
    md_extensions: +raw_attribute
bibliography: bibliography.bib
link-citations: yes

---

>  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
>  of the number of liars in "coin flip" style experiments. However, their method gives 
>  erroneous confidence intervals. I explain why and describe two better
>  ways to calculate probability distributions.

@@

1. Do not use the GSV confidence intervals.
2. If your N is reasonably large, say at least 100, you can safely use standard frequentist 
  confidence intervals and tests.
3. If your N is too small for point 2 to apply, it may be too small, full stop.
4. If increasing your N is not possible for whatever reason, consider using Bayesian methods to find
  confidence intervals and point estimates. To estimate differences between subgroups, consider
  empirical Bayes with a prior derived from the pooled sample.
